|

### 2020-05-08 documents/ovando-et-al-pop-effects-of-mpas.Rmd
making R v4.0.0 compliant

temp_plot <- validation_plot + 
  theme_1col + 
  theme(legend.position = "top") + 
  scale_fill_viridis(option = "C",
                     name = "Sims(#)",
                     guide = hgc <- guide_colorbar(frame.colour = "black",
                                                   ticks.colour = "black",
                                                   barwidth = unit(5,"lines")))

>>>>

temp_plot <- validation_plot + 
  theme_1col + 
  theme(legend.position = "top") + 
  scale_fill_viridis(option = "C",
                     name = "Sims(#)",
                     guide = hgc <- guide_colorbar(frame.colour = "black",
                                                   ticks.colour = "black",
                                                   barwidth = ggplot2::unit(5,"lines")))
